---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
pacman::p_load(tidyverse)
devtools::load_all()
# devtools::document()
# devtools::install()
```

## General Description

Executor orchestrates skript and emulates similar function to rstudio jobs, which can be executed in any rsession (even if rstudio is not running)

It entails one R6 class, which has a unique id. When executing a script, this unique_id is provided as an environment variable, so that two different executors can execute the same script at the same time, without mixing up (you can kill one without killing the other)

To create an instance, you simply need to specify a folder, where all skript logs will be saved and an executor_id. If you don't specify an id, a random one will be automatically attributed. 

```{r}
# Random ID
exec_model <- executor$new(folder = "test")
exec_model$ex_id

# Specified id
exec_model <- executor$new(folder = "test", exec_id = "xg15")
exec_model$ex_id


```
## Workflow

To execute a task, you need to perform two different actions: 

1. Adding the task to the executor
2. Starting the task

### Adding tasks

Differntiating these two steps will allow to stop and restart tasks (eventually, this will be used to implement schedules)

To add a task to an existing executor, you need to specify at least two arguments: 

+ a name: general description of the task, that will be used as an id internally
+ a script path: a path to the script that should be executed

You can eventually specify two further arguments

+ wd: the working directory for the script
+ env: environment variables that should be provided to the script. This can be used to parametrize scripts. 


```{r}
## Adding one task
exec_model$add_task(name = "LOL", script = "jobs/test.R", wd = getwd(), env = c("SYMBOL" = "LOL"))
exec_model$add_task(name = "LOL_Schedule", script = "jobs/test.R", wd = getwd(), env = c("SYMBOL" = "LOL_schedule"), infinite_loop = F, period = "2 min")
exec_model$add_task(name = "LOL_Schedule_day", script = "jobs/test.R", wd = getwd(), env = c("SYMBOL" = "LOL_schedule"), infinite_loop = F, period = "day", start = lubridate::as_datetime("2021-02-27 12:50:00", tz = "EST"))
## Adding a serie of task
c("LMFAO", "LOL") %>%
  purrr::walk(~{
    exec_model$add_task(name = .x, script = "jobs/test.R", wd = getwd(), env = c("SYMBOL" = .x))
  })

```

### Start/Stop tasks

Once a task is added, it can be start/stop. Remember that the name provided to the task it the internal id, hence it should be unique. 

```{r}
# Start task
exec_model$start_task(name = "LOL")
# Start all exising tasks
exec_model$start_all()

# Stop task
exec_model$stop_task(name = "LOL")
# Stop all tasks
exec_model$stop_all()

```

If you want to go to sleep and make sure, scripts restart if they break, you can start a forever loop, that will restart all failed tasks every `n` seconds. 

```{r}
sleep <- 60 # in seconds
# exec_model$keep_restarting(sleep = sleep) # forever loop, you'll need to stop this, once this is started

```

An overall log is stored in a log vector

```{r}
exec_model$log
```

## Retrieving information

### Meta information

To know the existing tasks in an executor, you can take a look at `exec_model$task`

```{r}
exec_model$tasks
```

If you're interested in which scripts are running, you can use the following function:

```{r}
exec_model$list_running_task()
```


```{r}
exec_model$list_running_task(next_run = T)
```

## Individual script information

Each script produces one output, saved in the log_folder specified when creating the executor. 

If you navigate to `"test"`, you will see that each script has one output file `LOL.txt`. 
If the script breaks and is restarted, the previous output is archived with a timestamp, so that we can know which error happened. So `LOL_111111111.txt` is the output of a previous run of the task `LOL`. Using this output, you can communicate with what's happening in the process. 

```{r}
exec_model$read_out(name = "LOL", n_tail = 50) %>% glimpse # Read the last 50 lines of the stream output of the task LOL

```

